The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes

### 2022-02-01 report/draft.Rmd
add full flow

[^5]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates. OA p. A-7 demonstrates the balance checks, demonstrating that only income is unbalanced, and therefore included as a covariate.

@@

So how does an ethnic and civic framing of the items `POP1` and `POP2` affect the latent construct of populism? 
A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix). 
Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 
This is not surprising, given that we varied the wording of `the people' only in two items of the full \@akkerman2014 item battery.

Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Table A.9 in the OA). 
In terms of model fit, both constructs show very similar goodness-of-fit statistics (i.e., CFI, BIC, RMSEA, and SRMR). Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`) -- for more information see OA Table A.8.

@@

We find that there are statistically significant differences between the two wordings. 
An ethnic conception of the people, overall, yielded more agreement with the items in question. 
This is effect is particularly pronounced for voters of the far right. 
The difference between an ethnic and a civic conception of the people was also only significant for respondents who adhered a moderate to high level of exclusive national identity. 
This finding is highly suggestive of the 'ethnic' interpretation of `the people' -- at least in the German language.

>>>>

[^5]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates. OA p. A-7 demonstrates the balance checks, demonstrating that only political interest and income are unbalanced, and therefore included as a covariate.

@@

So how does an ethnic and civic framing of the items `POP1` and `POP2` affect the latent construct of populism? 
A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix). 
Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 
This is not surprising, given that we varied the wording of `the people' only in two items of the full @akkerman2014 item battery. 
Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.

We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Table A.9 in the OA).
In terms of model fit, both constructs show very similar goodness-of-fit statistics (i.e., CFI, BIC, RMSEA, and SRMR). Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`) -- for more information see OA Table A.8. 
Yet, when looking at the additive scale (see Table **XX** in the OA), we see that the scale using the civic conception of the people has a statistically higher mean value compared to the ethnic conception.
The same holds for constructing a scale using the approach of @wuttke2020whole -- i.e. using the lowest value on one of the items that construe the latent construct.

@@

We find that there are statistically significant differences between the two wordings. 
An ethnic conception of the people, overall, yielded more agreement with the items in question. 
This is effect is particularly pronounced for voters of the far right, as well as for older voters. 
The difference between an ethnic and a civic conception of the people was also only significant for respondents who adhered a moderate to high level of exclusive national identity. 
This finding is highly suggestive of the 'ethnic' interpretation of `the people' -- at least in the German language.
